---
title: "Introdution to ImmuneSpaceR"
author: Renan Sauteraud
date: June 25, 2016
autosize: true
output:
  ioslides_presentation:
    widescreen: true
---
<style>
//h2{
//  color: white;
//}
//h3{
//  color: green;
//}
</style>

## Plan

- Instantiate connection
- Get data
- Cross assay
- Cross study
- Use case with external data
- Future

## .netrc

ImmuneSpace uses `Curl` for connections to the database. The login and password
information must be stored into a .netrc file.
```
machine   www.immunespace.org
login     bioc16@immunespace.org
password  pwd
```

For this workshop, we can write a temporary file that will be deleted at the end
of the session.
```{r}
library(ImmuneSpaceR)
write_netrc(login = "bioc16@immunespace.org", password = "pwd")
```


## Instantiate a connection {.smaller}

```{r CreateConnection}
con <- CreateConnection("SDY269")
con
```

## Get data


## Future
- Rework the instantiation to allow connection to a subset of studies 
    `CreateConnection(c("SDY61", "SDY269"))`
- Use <a href="https://www.immunespace.org/project/Studies/begin.view?">Data Finder</a> filter in R
- Integration of Rstudio to ImmuneSpace (spawn pre-filtered R sessions)
- Accept user made R/Rmd reports on ImmuneSpace
- Improve testing of both ImmuneSpaceR & ImmuneSpace
